Democracy, Public Support, and Measurement Uncertainty

### 2021-08-13 paper/dcpo_demsupport.Rmd
fix misspelling of "Uncertainty" throughout

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )

@@

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )

@@

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )

@@

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>%
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )
```

```{r plot-mainDCPOAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
type_model <-
    c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")

@@

```{r formatDCPOResult-AJPS}
result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertianty+ExpData"),
 mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))

@@

result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertianty+ExpData"),
 mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertianty+DCPO+ExpData")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))

@@

type_model <-
  c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")

>>>>

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
  )

@@

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
  )

@@

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
  )

@@

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertainty+DCPO+ExpData")) %>%
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertainty+DCPO+ExpData")) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
  )
```

```{r plot-mainDCPOAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
type_model <-
    c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")

@@

```{r formatDCPOResult-AJPS}
result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+ExpData"),
 mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))

@@

result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+ExpData"),
  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertainty+DCPO+ExpData")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+ExpData"),
 mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertainty+DCPO+ExpData")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))

@@

type_model <-
  c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")
